Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-23 paper-v1.tex
fix figure 1 ref

In the following sections we describe the architecture of the system and its building blocks.
\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:

>>>>

In the following sections we describe the architecture of the system and its building blocks.
\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart (See Figure \ref{fig:contracts}):
